---
title: "HW7_Yun_Young"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

```{r, echo=F, warning= FALSE, message= FALSE}
# A function for captioning and referencing images
library(tidyr)
library(dplyr)
library(foreach)
library(doParallel)
library(knitr)
library(kableExtra)


fig <- local({
    i <- 0
    ref <- list()
    list(
        cap=function(refName, text) {
            i <<- i + 1
            ref[[refName]] <<- i
            text
        },
        ref=function(refName) {
            ref[[refName]]
        })
})
```


#Problem 2
###a. a for loop to iterate through all data points calculating the summed squared difference between the data points and mean of the data.
Completed.
```{r, echo=F}
##Part a: Using for-loop go through each iteration of y to get SST.
set.seed(12345)
y <- seq(from=1, to=100, length.out = 1e8) + rnorm(1e8)

mean_y <- mean(y)
sum = 0

time_partA <- system.time(for(i in 1:length(y))
{
  sum = sum + (y[i] - mean_y)^2
})

```
###b. repeat part a, but use vector operations to effect the same computation
```{r, echo=F}
##Part b: Using a vector operations to get SST
time_partB <- system.time(sum_vector <- sum((y - mean_y)^2))

timetable <- data.frame(cbind(time_partA, time_partB))

kable(timetable, row.names = T, caption= "Time taken in Part A and B")
```
  
###c. repeat part a, but use dopar
I could not get it run properly
```{r, echo=F, eval=FALSE}
##Part c: uses 'foreach' and 'dopar' to compute, for each piece of y, the squared difference between y and its mean.
#Notice using '.combine' argument in 'foreach', the computed result gets summed up
library(foreach)
library(doParallel)

length_y <- length(y)
cl <- makeCluster(2)
registerDoParallel(cl)
system.time(SST <- foreach(i = 1:length(y) %dopar% ((y-mean_y)^2)))
stopCluster(cl)
```
###d. repeat part a, but use parSapply
I could not get it run properly
```{r, echo=F, eval=FALSE}
##Part d: uses 'parSapply' to get the above SST. To do so, 'func' was defined, which takes a variable and computes its squared difference.

func <- function(a)
{
  (a-mean(a))^2
}

cl <- makeCluster(2)
registerDoParallel(cl)

system.time(parSapply(cl, y, function(a) func(y)))

stopCluster(cl)


```

#Problem 3
```{r echo = F}
    #generate the data
    set.seed(1256)
    theta <- as.matrix(c(1,2), nrow =2)
    X <- cbind(1, rep(1:10,10))
    h <- X %*% theta + rnorm(100,0,0.2)
    
    theta0_current <- 0
    theta0_new <- 1
    theta1_current <- 0
    theta1_new <- 1
    alpha <- 0.0001
    tolerance <- 0.000001
    m <- length(h)
    

    ##I have fixed the code to do both updates in the same loop
    t4 <- system.time({
    while(abs(theta0_new-theta0_current)>tolerance & abs(theta1_new-theta1_current)>tolerance)
    {
          theta0_current <- theta0_new
          theta1_current <- theta1_new
          theta0_grad <- 0
          theta1_grad <- 0
          #foreach(i=1:m) %dopar% {}
          for(i in 1:m)
          {
            theta0_grad <- theta0_grad + theta0_current + theta1_current * X[i,2] - h[i]
            theta1_grad <- theta1_grad + theta0_current + (theta1_current * X[i,2] - h[i])*X[i,2]
          }
          
          theta0_new <- theta0_current - alpha/m * theta0_grad
          theta1_new <- theta1_current - alpha/m*theta1_grad
        }
    })
```


#Problem 4
###A. Impliment bootstrap algorithm using the data generated below for B=10,000.
Completed
```{r, echo=F}
###THis code uses foreach and dopar to estimate by bootstrap. First set 'bootbeta' matrix to store values of beta later accoding to b(=1000). Then, using foreach from 1 to b, do bootstrap for each. The bootstrap is done by samping accodingly with n with replacement and for each iteration generate 'bootx', 'booty' then use lm() to get beta. This data is stored in 'bootforeach', which gets unlisted and stored in the 'bootbeta' matrix. 

set.seed(1267)
n <- 200
X <- 1/cbind(1,rt(n,df=1),rt(n,df=1),rt(n,df=1))
beta <- c(1,2,3,0)
Y <- X %*% beta + rnorm(100,sd=3)
b <- 1000

bootbeta <- matrix(0, b, 5)

cl <- makeCluster(2)
registerDoParallel(cl)

t1 <- system.time(bootforeach <- foreach(i = 1:b) %dopar% 
{
  bootid <- sample(1:n, n, replace = T)
  bootx <- X[bootid, ]
  booty <- Y[bootid]
  bootfit <- coef(lm(booty~bootx))
  #bootbeta[i, ] <- coef(bootfit)
})

stopCluster(cl)


for(i in 1:b)
{
  bootbeta[i, ] <- unlist(bootforeach[i])
}

bootbeta <- select(data.frame(bootbeta),  c(1,3,4,5))
colnames(bootbeta) <- c("beta0", "beta1", "beta2", "beta3")

```
###B. Create a table of the result with the appropriate summary statistics.
```{r echo = F}
##This creates head and tail of bootbeta data and the summary statistics for the betas. 
kable(rbind(head(bootbeta), tail(bootbeta)), row.names = F, caption="Beta esitimation showing head/tail")
kable(summary(bootbeta), row.names = F, caption="Beta estimattion Summary")

```



###C. Create histograms of the distribution of $\hat\beta$'s. 
```{r echo=F}
##This code draws histograms of all the beta in one panel.
par(mfrow=c(2,2))
hist(bootbeta[1]$beta0, main = "Histogram of beta0")
hist(bootbeta[2]$beta1, main = "Histogram of beta1")
hist(bootbeta[3]$beta2, main = "Histogram of beta2")
hist(bootbeta[4]$beta3, main = "Histogram of beta3")

```
  
##Which parallelization method did you use?  
  I used foreach, dopar as my parallelization method.  
##What impediments did you encounter?  
  Using Forloop it was possible to use [i] as a tracking variable, but using foreach I could not use [i] as a variable because [i] does not change.   
##How long did it take?  
`r t1[3]` seconds is taken to do the foreach and dopar function.  